Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-05-23 sections/3algebras.tex
Typo in previous commit.
added todos in Prop 3.16

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

@@

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \Cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $E_n$-algebras from \cref{prop:framed_ndisk=En}.
\end{proof}

>>>>

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

@@

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \Cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \Cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \Cref{lem:double_slice} we can rewrite \Cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \Cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.

    {\color{red} \bf TODOs:} \cite[prop.2.22]{af_primer} is smooth, we need stratified.
    \begin{itemize} 
        \item It rests on \cite[Lemma 2.30]{af_primer} which is about what happens when you do a base change from $\mathsf{RFib}_{\disk_n}$ to $\mathsf{RFib}_{\disk_n^{\simeq}}$ where $-^\simeq$ takes the core. The same base change in the stratified setting will be allowed because we will still be working with right fibrations. Probably in the stratified core $\disk^\simeq$ basic disks with different stratifications disconnect into separate connected components.\footnote{Not "probably", but surely.} This should lead to a similar argument. 
        \item Then the following remark: a covering sieve $\mathscr{U}$ on $M$ being Weiss is exactly saying that the smallest sieve on $M$ containing $\{\mathrm{Conf}_i(U)_{\Sigma_i}\hookrightarrow\mathrm{Conf}_i(M)_{\Sigma_i}\}_{U\in\mathscr{U}}$ is a covering sieve on $\mathrm{Conf}_i(M)_{\Sigma_i}$.\footnote{Here $i$ is the number disks, fixed but arbitrary; $(-)_{\Sigma_i}$ makes the configurations unordered.} Then the fact that $\mathrm{Conf}_i(M)_{\Sigma_i}$ is Hausdorff and paracompact gives the desired equivalence. Something similar might hold in the stratified case but this is not obvious. Hopefully AFT already wrote it down somewhere. I vaguely remember a statement that conically-smooth stratified spaces have partitions of unity, possibly in their "Factorization homology I" paper. If so, it's either there or I'd guess in the local structures paper.
        \item In the first place, the replacement of $\mathsf{Cat}_\infty$ by $\mathsf{RFib}_{\disk_n}$ in the calculation needs to be check to be benign. This is probably something obvious and has (I'd say) least priority.
    \end{itemize}
\end{proof}

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
\end{proof}
